A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2016-10-10 doc/paper1-submission/paper4.tex
Update.

@@

We seek to assess the performance of our new supertree method by
comparing it to the supertree method of \cite{HinchliffEtAl2015}.  The
method of \cite{HinchliffEtAl2015} was used to construct the Open Tree
of Life v4 (\otl{}).  Therefore, in order to facilitate comparison, we 
applied our method to same input trees and taxonomy used by
\otl{}.  We used the same cleaning flags to trim the taxonomy and
input trees.  We refer to the resulting supertree as \otlprop{} since it was
constructed by applying the propinquity pipeline to the same inputs as
\otl{}.
The flag-cleaned version of OTT contained 2,424,255 leaves.  The
\otl{} supertree was constructed from 482 phylogenetic inputs,
containing a total of 45385 leaves, of which 41029 were unique.
After flag-cleaning and exemplification by propinquity, these trees contained 40323
unique tips.

@@

\subsection{splits}
We ran propinquity on the same input
trees used to construct version Open Tree version 4. Unlike the version
4 tree, the tree from propinquity contained no unsupported nodes or
unnecessary polytomies. The number of displayed input splits increased
from 35,518 (for version 4) to 39,639; an 11.2\% increase. The number
of input splits that do not conflict with the summary tree, but are
not incorporated dropped from 2718 to 0. The number of input splits
that conflict with the phylogeny dropped from 2760 to 1357, a decrease
of 1357, or 49.2\%. %

>>>>

We seek to assess the performance of our new supertree method by
comparing it to the supertree method of \cite{HinchliffEtAl2015}.  The
method of \cite{HinchliffEtAl2015} was used to construct the Open Tree
of Life v4 (\otl{}).  Therefore, in order to facilitate comparison, we 
applied our method to same input trees and taxonomy used by
\otl{}.  We used the same cleaning flags to trim the taxonomy and
input trees.  We refer to the resulting supertree as \otlprop{} since it was
constructed by applying the propinquity pipeline to the same inputs as
\otl{}.

@@

The flag-cleaned version of OTT contained 2,424,255 leaves.  The
\otl{} supertree was constructed from 482 phylogenetic inputs,
containing a total of 45385 leaves, of which 41029 were unique.
After flag-cleaning and exemplification by propinquity, these trees contained 40323
unique tips.

@@

% table

% outputs - representation of input trees
% outputs - annotations

% conflicts in v4: 2760
% conflicts in v4propr: 1357

% displayed in v4: 35,518
% displayed in v4propr: 39,639

% # of input splits represented by v4, but not v4prop
% # of input splits represented by v4prop, but not v4
% # of input splits represented by v4 and v4prop

\subsection{splits}

\begin{tabular}{lcccccc}
 & supported\_by & partial\_path\_of & terminal & conflicts\_with & resolves & resolved\_by\tabularnewline
\hline 
OTLv4 & 34,595 & 923 & 45,385 & 2760 & 473 & 2718\tabularnewline
\hline 
\textendash{} only & 745 & 54 & 0 & 2055 & 0 & 2718\tabularnewline
\hline 
OTLv4/propinquity & 38,521 & 1,118 & 45,385 & 1,357 & 515 & 0\tabularnewline
\hline 
\textendash{} only & 4,671 & 249 & 0 & 652 & 42 & 0\tabularnewline
\hline 
\end{tabular}

We ran propinquity on the same input
trees used to construct version Open Tree version 4. Unlike the version
4 tree, the tree from propinquity contained no unsupported nodes or
unnecessary polytomies. The number of displayed input splits increased
from 35,518 (for version 4) to 39,639; an 11.2\% increase. The number
of input splits that do not conflict with the summary tree, but are
not incorporated dropped from 2718 to 0. The number of input splits
that conflict with the phylogeny dropped from 2760 to 1357, a decrease
of 1357, or 49.2\%. %
